First exclusive Deeply Virtual Compton Scattering measurement off bound nucleon in $^4$He

### 2018-06-26 eg6-letters/incoherent/incoherent_prl.tex
more cleaning

Following the cross section decomposition provided in \cite{Belitsky:2001ns}, 
the different components can be expressed in terms of Fourier coefficients 
associated with $\phi$-harmonics, where $\phi$ is the angle between the 
leptonic and the hadronic planes of the reaction. At leading-twist, the 
beam-spin asymmetry can be simplified as: 
\begin{equation}
   A_{LU}(\phi) = \frac{a_{0}\sin(\phi)}{1+a_{1}\cos(\phi)+a_{2}\cos(2\phi)}
   \label{eq:alu-simp}
\end{equation}
where the parameters $a_{0,1,2}$ are combinations of the above mentioned Fourier 
coefficients. The $\sin(\phi)$ harmonic is dominant in $A_{LU}$ 
and is proportional to the following combination of Compton form factors (CFF) 
\cite{Guidal:2013rya}
\begin{equation}
   A_{LU}^{\sin\phi} \propto \operatorname{Im}( F_1 \mathcal{H}- \frac{t}{4M^2} 
   F_2 \mathcal{E}+ \frac{x_B}{2}(F_1+F_2)\tilde{\mathcal{H}})
\end{equation}
where $F_1$ and $F_2$ are the Dirac and Pauli form factors and $x_B$ the 
Bjorken scaling variable. The real and the imaginary parts of the CFF 
$\mathcal{H}$ relate to the GPD $H$ as  
\begin{align}
   \Re(&\mathcal{H}) = \mathcal{P} \int_{0}^{1}dx[H(x,\xi,t)-H(-x,\xi,t)] \, 
   C^{+}(x,\xi) \\
   \Im(&\mathcal{H}) = - \pi [H(\xi,\xi,t)-H(-\xi,\xi,t)],
\end{align}
with $\mathcal{P}$ the Cauchy principal value integral and $C^{+}$ a 
coefficient function defined as $(1/(x-\xi) + 1/(x+\xi))$, there $\xi$ is the 
skewing factor and can be
related to $x_B$ by $\xi\approx {{x_B}\over{2-x_B}}$. Similar expressions apply 
for the GPDs $E$, $\widetilde{H}$, and $\widetilde{E}$.

@@

In the kinematical domain of our experiment, the dominant contribution to the 
beam-spin asymmetry comes from the GPD $H$ \cite{Guidal:2013rya} as the $\phi$ 
dependence of $A_{LU}$ gives access to the real and imaginary part of the CFF 
$\mathcal{H}$ through the parameters $a_0$, $a_1$, and $a_2$ of equation \ref{eq:alu-simp}. The studies of  
the free proton $A_{LU}$ measurements, \cite{Girod:2007aa}, have 
shown that the the pure DVCS contribution, $cos(2\phi)$ term ($a_2$), is suppressed and compatible with zero.  
{\bf Raphael: This paragraph is very confusing, is it true that a1 and a2 are 
dominated by H? Do we have equivalents of eq. 3 for those? I actually did not find
it in ref 31, which we are referring and we are also not using the same definition
of Im(H)...}

>>>>

Following the cross section decomposition provided in \cite{Belitsky:2001ns}, 
the different components can be expressed in terms of Fourier coefficients 
associated with $\phi$-harmonics, where $\phi$ is the angle between the 
leptonic and the hadronic planes of the reaction. At leading-twist, the 
beam-spin asymmetry can be simplified as: 
\begin{equation}
   A_{LU}(\phi) = \frac{a_{0}\sin(\phi)}{1+a_{1}\cos(\phi)+a_{2}\cos(2\phi)}
   \label{eq:alu-simp}
\end{equation}
where the parameters $a_{0,1,2}$ are combinations of the above mentioned Fourier 
coefficients. The $\sin(\phi)$ harmonic is dominant in $A_{LU}$ 
and is proportional to the following combination of Compton form factors (CFF) 
\cite{Guidal:2013rya}
\begin{equation}
   a_{0} \propto \operatorname{Im}( F_1 \mathcal{H}- \frac{t}{4M^2} F_2 
   \mathcal{E}+ \frac{x_B}{2}(F_1+F_2)\tilde{\mathcal{H}})
\end{equation}
where $F_1$ and $F_2$ are the Dirac and Pauli form factors and $x_B$ the 
Bjorken scaling variable. The real and the imaginary parts of the CFF 
$\mathcal{H}$ relate to the GPD $H$ as  
\begin{align}
   \Re(&\mathcal{H}) = \mathcal{P} \int_{0}^{1}dx[H(x,\xi,t)-H(-x,\xi,t)] \, 
   C^{+}(x,\xi) \\
   \Im(&\mathcal{H}) = - \pi [H(\xi,\xi,t)-H(-\xi,\xi,t)],
\end{align}
with $\mathcal{P}$ the Cauchy principal value integral and $C^{+}$ a 
coefficient function defined as $(1/(x-\xi) + 1/(x+\xi))$, there $\xi$ is the 
skewing factor and can be
related to $x_B$ by $\xi\approx {{x_B}\over{2-x_B}}$. Similar expressions apply 
for the GPDs $E$, $\widetilde{H}$, and $\widetilde{E}$.

@@

In the kinematical phase-space of our experiment, the GPD $H$ dominants the 
contribution in the beam-spin asymmetry over the other three GPDs. Therefore, 
the $\phi$ dependence of $A_{LU}$ gives a direct access to the real and 
imaginary part of the CFF $\mathcal{H}$ through the parameters $a_0$, $a_1$, 
and $a_2$ of equation \ref{eq:alu-simp}. The studies of  the free proton 
$A_{LU}$ measurements, \cite{Girod:2007aa}, have shown that the the pure DVCS 
contribution, $cos(2\phi)$ term ($a_2$), is suppressed and compatible with 
zero.

%{\bf Raphael: This paragraph is very confusing, is it true that a1 and a2 are 
%dominated by H? Do we have equivalents of eq. 3 for those? I actually did 
%notfind it in ref 31, which we are referring and we are also not using the 
%same definition of Im(H)...}
